\toolnameend: A Tool for Visualizing Patterns of Spreadsheet Function Combinations

### 2016-08-13 doc/paper.tex
Another glyph revision

		\item  \vspace{.25cm}
		$\vcenter{\hbox{\includegraphics[scale=.75]{glossary-lightblue}}}$
		\textbf{Optional argument trees} are variations of trees that show only
		formulae with a specific number of arguments. For example, the function
		\texttt{AND} can take any number of arguments, up to 255. By default, the tree
		shows data from \texttt{AND} functions with any number of arguments, but these
		trees, which have argument nodes of a lighter blue color, can show how
		\texttt{AND} was used when \textit{only} two arguments were passed into it, or
		\textit{only} four, and so on. See Figure~\ref{fig:optional} for how the data
		between tree types differs.
	\end{itemize}

	\begin{figure}[h] 
		\centering
		\begin{subfigure}
		  \centering
		  \includegraphics[width=.4\linewidth]{comparison1}
		\end{subfigure}%
		\begin{subfigure}
		  \centering
		  \includegraphics[width=.4\linewidth]{comparison2}
		\end{subfigure} 
		\includegraphics[]{comparison-ss} \caption{The
			contents of the default tree (left) and the optional argument trees (right)}
		\label{fig:optional} \end{figure}

>>>>

		\item  \vspace{.25cm}
		$\vcenter{\hbox{\includegraphics[scale=.75]{glossary-lightblue}}}$
		\textbf{Optional argument trees} are variations of trees that show only
		formulae with a specific number of arguments. For example, the function
		\texttt{AND} can take any number of arguments, up to 255. By default, the tree
		shows data from \texttt{AND} functions with any number of arguments, and an
		example of the \texttt{AND} tree with sample contents is shown on the left of
		Figure~\ref{fig:optional}. Optional argument trees, however, have argument
		nodes of a lighter blue color and show how \texttt{AND} was used when
		\textit{exactly} two arguments were passed into it, or \textit{exactly} four,
		without including uses of this function with any other number of arguments.
	\end{itemize}

	\begin{figure}[h] 
		\centering
		\begin{subfigure}
		  \centering
		  \includegraphics[width=.4\linewidth]{comparison1}
		\end{subfigure}%
		\begin{subfigure}
		  \centering
		  \includegraphics[width=.4\linewidth]{comparison2}
		\end{subfigure} 
		\includegraphics[]{comparison-ss} \caption{The
			contents of the default tree (left) and the optional argument tree with 4 arguments (right)}
		\label{fig:optional} \end{figure}
